Large-scale peer-to-peer network for mobile platforms: Challenges and Experiences\\

### 2019-02-10 paper.tex
Added all figs and experimental results

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

In our approach, since the origin of weather information is the
Weather Channel service, digital signatures can be attached to all
weather alerts broadcast from the service. The mobile application is
distributed with the corresponding public key so that digital
signatures from the service can be verified. If a message fails such a
verification, it is discarded and not forwarded any further.
\section{Experimental Results}
\label{sec:eval}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{figs/e2e_latency}}
\caption{End-to-end latency}
\label{fig:e2e}
\end{figure}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{array,multirow,graphicx}
\usepackage{float}
\usepackage{algorithmic}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

In our approach, since the origin of weather information is the
Weather Channel service, digital signatures can be attached to all
weather alerts broadcast from the service. The mobile application is
distributed with the corresponding public key so that digital
signatures from the service can be verified. If a message fails such a
verification, it is discarded and not forwarded any further.

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{figs/android_ios}}
\caption{Interoperability matrix between Android and iOS devices over BTLE}
\label{fig:android_ios}
\end{figure}

\begin{table}[H]
\caption{Android protocols and range results}
\centering
\begin{tabular}{|c|l|r|r|r|c|l|}
\hline
& \multicolumn{1}{c|}{Protocol} & \multicolumn{1}{c|}{Throughput} & \multicolumn{1}{c|}{Battery} & \multicolumn{1}{c|}{Range} & \multicolumn{1}{c|}{iOS} & \multicolumn{1}{c|}{Issues}\\
&                               & \multicolumn{1}{c|}{Avg. kbps}  & \multicolumn{1}{c|}{per hour} & \multicolumn{1}{c|}{LoS ft} &                  &                            \\
\hline
\parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{WiFi}}} & \textbf{DNS} & 0.2 & 2\% & 600 & No & \\
& WiDi & 2000 & 3\% & 600 & No & Needs DNS\\
& Hotspot & 2000 & 5\% & 600 & No & Permission\\
\hline
\parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{BT}}} & Classic & 50 & 2\% & 600 & No & Unstable\\
& \textbf{Nearby} & 50 & 2\% & 600 & No & \\
& \textbf{BTLE} & 50 & 2\% & 600 & Yes & \\
\hline
\end{tabular}
\end{table}

\begin{table}[H]
\caption{iOS protocols and range results}
\centering
\begin{tabular}{|c|l|r|r|r|c|l|}
\hline
& \multicolumn{1}{c|}{Protocol} & \multicolumn{1}{c|}{Throughput} & \multicolumn{1}{c|}{Battery} & \multicolumn{1}{c|}{Range} & \multicolumn{1}{c|}{Android} & \multicolumn{1}{c|}{Issues}\\
&                               & \multicolumn{1}{c|}{Avg. kbps}  & \multicolumn{1}{c|}{per hour} & \multicolumn{1}{c|}{LoS ft} &                  &                            \\
\hline
\parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{WiFi}}} & Bonjour & 0.2 & 5\% & 200 & No & Battery\\
& MPC & 2000 & 5\% & 200 & No & Battery\\
& WiDi & 2000 & 5\% & 200 & No & Battery\\
\hline
& \textbf{BTLE} & 50 & 2\% & 800 & Yes & \\
\hline
\end{tabular}
\end{table}

%
\section{Experimental Results}
\label{sec:eval}
%

%
\subsection{Pilot test results}
\label{sec:romania}
%
\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{figs/romania_latency}}
\caption{Latency results from a 25-user pilot}
\label{fig:romania_lat}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{figs/romania_activity}}
\caption{MNA activity during the pilot}
\label{fig:romania_act}
\end{figure}

About 13\% of the messages were received at least once (depends on
density of users in the building). Users actively used the devices for
~5\% of the time p2p NSD achieved lower end-to-end latencies than BT
Classic, perhaps due to its broadcast model and wide support across
devices. Packet sizes did not affect single-hop latencies on p2p DNS,
perhaps because most of the messages fit within single advert. Packet
sizes did not affect single-hop latencies on BT Classic, perhaps
because Bluetooth has a much higher bandwidth 2 out of 25 devices have
their clocks set wrong (confusing latency results). More than 10\% of
the messages were received in the last 5 min of message expiry,
implying messages were discarded due to expirty, even when they did
not reach all devices

%
\subsection{Automated test results}
\label{sec:automated}
%
\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{figs/variety_e2e_latency}}
\caption{Comparison of WiFi and Bluetooth interfaces in terms of
  end-to-end latency}
\label{fig:variety_e2e}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{figs/variety_hops}}
\caption{Comparison of WiFi and Bluetooth interfaces in terms of
  network topology}
\label{fig:variety_hops}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{figs/e2e_latency}}
\caption{Comparison of WiFi and Bluetooth Nearby interfaces in terms
  of end-to-end latency}
\label{fig:e2e}
\end{figure}
